Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-03-07 latex/comp_or.tex
Shims and mpShims 50 run
scenarios = [6] # infeasible solutions with Shims............
First version of second paper

We also contributed by carrying out multiple experiments with the Shims heuristic on synthetic data based on real data from the {\it Brazilian Air Force} transportation history and a new procedure to minimize the distance from the next node destined pallet to the ramp door.

We converted Shims into a process-based parallel computing heuristic that quickly finds good solutions for a wide range of problem sizes, an essential contribution as it surpassed all Shims results.

@@

\begin{keyword}
Air Cargo \sep Air Palletization \sep Weight and Balance \sep Pickup and Delivery \sep Vehicle Routing \sep Parallel computing
\end{keyword}

@@

As can be seen, so far \cite{LurkinSchyns2015} is the only work that simultaneously addresses an air cargo (WBP) and a flight itinerary (PDP) sub-problem. Although it is innovative, strong simplifications were imposed by the authors: in relation to loading, APP was ignored; with regard to routing, it is assumed a pre-defined flight plan restricted to two legs. It is important to note that these authors consider an aircraft with two doors, and the minimization of loading and unloading (MLU) costs at the intermediate node was modelled through a container sequencing problem. Referring directly to this work, \cite[p. 409]{BrandtStefan2019} comment: {\it However, not even these sub-problems are acceptably solved for real-world problem sizes or the models omit some practically relevant constraints}.

@@

		\includegraphics[scale=0.25]{Images/shims.png}
		\captionof{figure}{Shims of various thicknesses}
		\small\textsuperscript{Source: www.mscdirect.com/product/details/70475967}
		\label{fig:shims}

@@

$3^{st}$ - Shims construction and best Shims selection

@@

\subsubsection{Shims first phase}

@@

\subsubsection{Shims second phase: improvement on minimizing CG deviation}

@@

\subsubsection{Shims third and fourth phases}

@@

Algorithm \ref{alg:getBestShims} describes the procedure do get the best Shims, the best subset of edges to fill each pallet gap. This algorithm follows the logic of the {\it First-Fit Decreasing} algorithm as described by \cite{JohnsonGarey1985}.

@@

The average tour values were presented for $f$ and, for the runtime, the worst result obtained. To facilitate the comparison between the methods, we added a last column in these tables, where two values are indicated:
\begin{itemize}
	\item {\bf Normalized}: value between 0 and 1, which corresponds to the ratio between the sum of $f$\/ values obtained by the method in all scenarios and the sum of the best values obtained among all methods in all scenarios. The higher the value of {\bf Normalized}, the closer the method approached the best solutions found.
	\item {\bf Speed-up}: ratio of the sums of the worst runtimes of all scenarios and the sum of the method runtimes in all scenarios. The method with the highest {\bf Speed-up}\/ is the fastest.
\end{itemize}

@@

\begin{table}[H]
\centering
\caption{Volume surpluses, methods and scenarios results}  \label{tab:results}
\footnotesize
%\scriptsize
\begin{tabular}{crcccccccc}
\toprule
&                          &                     &\multicolumn{6}{c}{\bf Scenarios}                                                                        &{\bf Normalized}\\
                                                 \cmidrule{4-9}		
{\it surplus}         & {$method$}               & {\bf Results}      &{\bf 1}      &{\bf 2}      &{\bf 3}      &{\bf 4}      &{\bf 5}       &{\bf 6}      &{\bf Speed-up} \\
\toprule

\multirow{7}{*}{$1.2$}&\multirow{1}{*}{ $Gurobi$}& $f$                &{\bf 11.22}   &{\bf 7.88}   & 10.25      & 11.02       & 11.88        & 12.92       & 0.90 \\% 6484    7222

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $Shims$}                       & $f$                & 9.66         &  6.38       &  9.55       &  11.12      &  12.37      &   12.03      & 0.85 \\%6111
&                                                & {\it run-time (s)} &  < 1         &  5          &    11       &   43        &  128        &  835        &  1.0 \\%1023

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $mpShims$}                     & $f$                & 11.03        & 7.43        &{\bf 12.58}  &{\bf 13.08}  &{\bf 14.02}  & {\bf 13.44}  &  {\bf 0.99}\\%7158

&                                                & {\it run-time (s)} &  < 1         &  2          &    4        &  15         &  47         & 295          &  {\bf 2.8}\\%364

@@

\multirow{7}{*}{$1.2$}&\multirow{1}{*}{ $Gurobi$}& $f$                &{\it 0}   &{\it 0}   &{\it 0}  &{\it 0}  &{\it 0}   &{\it 0}  & {\it 1.00} \\% 6607

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $Shims$}                       & $f$                & 13.71       &  9.06       &  13.54      &  15.21      &   17.09     &  17.15       & 0.84\\%
&                                                & {\it run-time (s)} &  < 1        &  3          &    6        &   24        &   70        &  419         & 5.9\\%

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $mpShims$}                     & $f$                & {\bf 16.85} & 10.65       & {\bf 16.68} & 17.05       & 19.72       & {\bf 18.53}  & 0.98\\%
&                                                & {\it run-time (s)} &  < 1        &  2          &    3        &   10        &   28        &   173        & {\bf 14.1}\\%

\midrule
\multirow{7}{*}{$1.2$}&\multirow{1}{*}{ $Gurobi$}& $f$                &{\it 0}   &{\it 0}   &{\it 0}  &{\it 0}  &{\it 0}   &{\it 0}  & {\it 1.00} \\% 6607

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $Shims$}                       & $f$                & 20.42       &  13.89      &  20.36      &  22.71      &   25.13     & 24.69        & 0.86\\%
&                                                & {\it run-time (s)} &  < 1        &  4          &    7        &   30        &   85        &  501         & 7.7\\%

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $mpShims$}                     & $f$                & 23.12       & 14.89       & 22.08       & 23.96       & 26.98       & 25.29        &  0.93\\%
&                                                & {\it run-time (s)} &  < 1        &  2          &    3        &   12        &   33        &  203         & {\bf 19.0}\\%

@@

The upper bound is the objective function value of an LP relaxation of the problem, proving that no integer feasible solution of larger objective value than this value can exist.

In an attempt to find the upper bound for $f$, we solved all scenarios and instances with {\it Gurobi} in a linear relaxed model. We applied a time limit of 60s in the expectation that it would be enough for {\it Gurobi} to determine the upper bounds. This is good for the reader to have an idea of the real performance differences between serial and parallel {\it Shims}.

Most of the {\it mpShims} $f$ results are superior to the upper bound found because they are not really the upper bound. As {\it Gurobi} runtime was limited, it did not have enough time to update the upper bound. But it is a good reference to compare {\it Shims} and {\it mpShims} performances.

As to the speedup, on average, {\it mpShims} was 2.8 times faster than {\it Shims}. Theoretically, it could be more, but due to the burden of sharing the CG deviation and the list of items among the processes for reading and writing, the runtime management to hinder race condition limited {\it mpShims} performance.

@@

xxxxx

We added an important contribution by favoring ground operations reducing in 29\%, in average, the distances pallets will be moved on disembarking operations.

Another important contribution is that we employed the {\it iRace} package to fine tune the meta-heuristics parameters, guaranteeing the best possible performance for the instances under training and testing.

>>>>

We also contributed by carrying out multiple experiments with the {\it Shims} heuristic on synthetic data based on real data from the {\it Brazilian Air Force} transportation history and a new procedure to minimize the distance from the next node destined pallet to the ramp door.

We converted {\it Shims} into a process-based parallel computing heuristic that quickly finds good solutions for a wide range of problem sizes, an essential contribution as it surpassed all {\it Shims} results.

@@

\begin{keyword}
Air Cargo \sep Air Palletization \sep Weight and Balance \sep Pickup and Delivery \sep Parallel computing \sep iRace
\end{keyword}

@@

As can be seen, so far \cite{LurkinSchyns2015} is the only work that simultaneously addresses an air cargo (WBP) and a flight itinerary (PDP) sub-problem. Although it is innovative, strong simplifications were imposed by the authors: in relation to loading, APP was ignored; with regard to routing, it is assumed a pre-defined flight plan restricted to two legs. It is important to note that these authors consider an aircraft with two doors, and the minimization of loading and unloading costs ({\bf MLU}) at the intermediate node was modelled through a container sequencing problem. Referring directly to this work, \cite[p. 409]{BrandtStefan2019} comment: {\it However, not even these sub-problems are acceptably solved for real-world problem sizes or the models omit some practically relevant constraints}.

@@

		\includegraphics[scale=0.25]{Images/shims.png}
		\captionof{figure}{{\it Shims} of various thicknesses}
		\small\textsuperscript{Source: www.mscdirect.com/product/details/70475967}
		\label{fig:shims}

@@

$3^{st}$ - {\it Shims} construction and best {\it Shims} selection

@@

\subsubsection{{\it Shims} first phase}

@@

\subsubsection{{\it Shims} second phase: improvement on minimizing CG deviation}

@@

\subsubsection{{\it Shims} third and fourth phases}

@@

Algorithm \ref{alg:getBestShims} describes the procedure do get the best {\it Shims}, the best subset of edges to fill each pallet gap. This algorithm follows the logic of the {\it First-Fit Decreasing} algorithm as described by \cite{JohnsonGarey1985}.

@@

The average tour values were presented for $f$ and, for the runtime, the worst result obtained. To facilitate the comparison between the methods, we added a last column in these tables, where two values are indicated:
\begin{itemize}
	\item {\bf Normalized}: value between 0 and 1, which corresponds to the ratio between the sum of $f$\/ values obtained by the method in all scenarios and the sum of the best values obtained among all methods in all scenarios. The higher the value of {\bf Normalized}, the closer the method approached the best solutions found.
	\item {\bf Speedup}: ratio of the sums of the worst runtimes of all scenarios and the sum of the method runtimes in all scenarios. The method with the highest {\bf Speed-up}\/ is the fastest.
\end{itemize}

@@

\begin{table}[H]
\centering
\caption{Volume surpluses, methods and scenarios results}  \label{tab:results}
\footnotesize
%\scriptsize
\begin{tabular}{crcccccccc}
\toprule
{\bf Volume}     &  {\bf Resolution}   &                              &\multicolumn{6}{c}{\bf Scenarios}                                                   &{\bf Normalized}\\
                                                \cmidrule{4-9}		
{\it surplus}    & {\it method}        & {\bf Results}                &{\bf 1}      &{\bf 2}      &{\bf 3}      &{\bf 4}      &{\bf 5}       &{\bf 6}      &{\bf Speedup} \\
\toprule

%\specialcell{$Volume$\\$surplus$}

\multirow{6}{*}{$1.2$}&\specialcell{$Relaxed$\\$Gurobi$}& $f$         &{\it 11.22}   &{\it 7.88}   &{\it 10.25} &{\it 13.34}  &{\it 14.30}   &{\it 12.92}       & 1.00 \\% 6845

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $Shims$}                       & $f$                & 9.66         &  6.38       &  9.55       &  11.12      &  12.37      &   12.03      & 0.89 \\% 6111
&                                                & {\it run-time (s)} &  < 1         &  5          &    11       &   43        &  128        &  835         &  1.0 \\% 1023

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $mpShims$}                     & $f$                & 11.03        & 7.43        & 10.05       & 13.08       & 14.02       &  12.66       & 0.99\\% 6827

&                                                & {\it run-time (s)} &  < 1         &  2          &    4        &  15         &  47         & 295          &  {\bf 2.8}\\% 364

@@

\multirow{6}{*}{$1.5$}&\specialcell{$Relaxed$\\$Gurobi$}& $f$         &{\it 15.17}   &{\it 10.98}  &{\it 17.80}  &{\it 16.92}  &{\it 19.63}   &{\it 18.62}  & {\it 1.00} \\% 9912

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $Shims$}                       & $f$                & 13.70        &  9.07       &  13.70      &  15.43      &   17.19     &  17.24       & 0.87 \\%8633
&                                                & {\it run-time (s)} &  < 1         &  4          &    7        &   26        &   81        &  520         & 1.0\\% 639

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $mpShims$}                     & $f$                & 14.82        & 10.45       & 17.45       &{\bf 16.92}  & 19.27       & 18.30        & 0.98\\%9721
&                                                & {\it run-time (s)} &  < 1         &  2          &    3        &    12       &   38        &   236        & {\bf 2.2}\\% 292

\midrule
\multirow{6}{*}{$2.0$}&\specialcell{$Relaxed$\\$Gurobi$}& $f$         &{\it 23.11}   &{\it 16.74}  &{\it 23.63}  &{\it 24.33}  &{\it 26.22}  &{\it 25.80}   & {\it 1.00} \\% 13983

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $Shims$}                       & $f$                &   20.42      &   13.90     &  20.30      &  22.96      &   25.28     &   24.81      & 0.91\\% 12767
&                                                & {\it run-time (s)} &  2           &  9          &    17       &   68        &   206       &  1216        & 1.0\\% 1518

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $mpShims$}                     & $f$                &  22.66       &  15.41      &  23.17      &  23.37      &  23,91      &  25.25       &  0.96\\% 13377
&                                                & {\it run-time (s)} &  2           &  3          &    5        &   20        &   64        &  398         & {\bf 2.8}\\% 544

@@

The upper bound is the objective function value of a linear programming relaxation of the problem, demonstrating that no integer viable solution can have an objective value greater than this.

We solved all scenarios and instances with Gurobi in a relaxed linear model, {\it Relaxed Gurobi}. This is good for the reader to have an idea of the real performance differences between serial and parallel {\it Shims}.

We were lucky that {\it mpShims} touched the edge of the polyhedron that bounds the feasible region, it found the optimal solution in volume $surplus = 1.5$, scenario {\bf 4}.

{\it mpShims} had a quality performance very close to the {\it Relaxed Gurobi} upper bound solution, and, as to the {\bf Speedup}, on average, mpShims was 2.6 times faster than {\it Shims}. Theoretically, it could be more, but due to the burden of sharing the CG deviation and the list of items among the processes (pallets) for reading and writing, the runtime {\it race condition} management limited {\it mpShims} performance.

{\it When threads or processes attempt to simultaneously access a shared resource, and the accesses can result in an error, we often say the program has a race condition, because the threads or processes are in a "race" to carry out an operation.} \cite[p. 53]{Pacheco:2020}.

@@

In this work we dealt with a hard problem, named {\it Air Cargo Load Planning with Routing, Pickup, and Delivery Problem} considering standardized pallets in fixed positions, obeying the center of gravity constraints, delivering each item to its destination, and minimizing fuel consumption costs.

We converted \cite{MesquitaSanches2023} {\it Shims} into a process-based parallel computing heuristic, which we called {\it Multiprocessing Shims} or {\it mpShims}, that quickly finds good solutions for a wide range of problem sizes, an essential addition as it surpassed all {\it Shims} results, our first contribution.

We also carryed out 126 experiments with each method on synthetic data based on real data from the {\it Brazilian Air Force} transportation history.

We added another important contribution by favoring ground operations reducing in 29\%, in average, the distances pallets will be moved on disembarking operations, our second contribution.

Another important contribution is that we employed the {\it iRace} package \citep{LopezIbanezManuel2016} to fine tune the meta-heuristics parameters, guaranteeing the best possible performance for the instances under training and testing.
